---
title: "L15 Tables 2"
subtitle: "Data Visualization (STAT 302)" 
author: "YOUR NAME"
pagetitle: "L15 YOUR NAME"
date: today

format:
  html:
    toc: true
    toc-location: left
    embed-resources: true
    code-fold: show
    link-external-newwindow: true
    fig-dpi: 300

execute:
  warning: false

from: markdown+emoji 
reference-location: margin
citation-location: margin
html-table-processing: none
---

::: {.callout-tip icon=false}

## Github Repo Link

To link to your github **repo**sitory, appropriately edit the example link below. Meaning replace `https://your-github-repo-url` with your github repo url. Suggest verifying the link works before submitting.

[https://your-github-repo-url](https://your-github-repo-url)

:::

::: {.callout-important}

This is an optional lab, not a bonus lab. Meaning there are no bonus points.

:::

## Overview

The goal of this lab is to explore interactive tables with the `DT` and `reactable` packages. Interactive tables are particularly useful if you are displaying tables in an app.

The `gt` package added interactive elements with `opt_interactive()`. While there are no exercises for this, we would suggest trying to build the interactive tables with just `gt` options. It is unlikely you will be able to reproduce everything, but it would be good practice and it will help you decide when you need to switch from `gt` to a more advance interactive package.

## Dataset

We will be using the `pizzaplace` dataset included in the `gt` package and the `movie_ratings.rds` dataset, which should be placed into your `data/` subdirectory.

```{r}
#| label: load-pkgs-data

# load package(s)

# load data
```

## Exercise 1

Using the `pizza_sales` dataset derived from the `pizzaplace` dataset, recreate the following graphic as precisely as possible.

```{r}
#| label: ex-1
#| eval: false

# data wrangling
pizza_sales <- pizzaplace |> 
  summarize(
    number_sold = n(),
    profit = sum(price),
    .by = c(name, type)
  )
```

*Hints:*

-   `DT` package
-   set the page length to 8 entries
-   format Number Sold so that it is rounded
-   format Revenue as currency
-   backgroundColor for `"chicken"` is `"lightblue"`
-   example: <https://rstudio.github.io/DT/>

::: {.callout-tip icon=false}

## Solution

YOUR SOLUTION HERE

:::

## Exercise 2

Using the `movie_ratings` dataset, recreate the following graphic as precisely as possible. The `bar_chart` function created below is useful for making bar charts within cells.

*Hints:*

-   `reactable` package
-   striped and filterable
-   columns are changed within `column = list(...)`
-   `cell = function(value) {bar_chart(...) }`
-   `theme` argument equals `reactableTheme()`
    -   `backgroundColor = "#e6e6e6"`,
    -   `borderColor = "#fc5185"`,
    -   `stripedColor = "#b3e6ff"`,
    -   `borderWidth = "3px"`
-   Helpful links:
    -   <https://glin.github.io/reactable/>
    -   <https://glin.github.io/reactable/articles/examples.html>


::: {.callout-tip icon=false}

## Solution

```{r}
#| label: ex-2
#| eval: false

# function to make bar chart
bar_chart <- function(
  label,
  width = "100%",
  height = "16px",
  fill = "#00bfc4",
  background = NULL
) {
  bar <- div(style = list(
    background = fill,
    width = width, height = height
  ))
  chart <- div(
    style = list(
      flexGrow = 1,
      marginLeft = "8px",
      background = background
    ),
    bar
  )
  div(
    style = list(display = "flex", alignItems = "center"),
    label, chart
  )
}
```

:::